<style>
body {
    overflow: scroll;
}
</style>
---
title: "AstralMart"
output: ioslides_presentation

---

### By: ALEXANDR SURIN

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#library
library(flexdashboard)
library(tidyverse)
library(dplyr)
library(highcharter)
library(plotly)
library(lubridate)
#library maps
library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)
#libary machine learning
library(e1071)
library(MASS)
library(tree)
library(randomForest)
library(gbm)


```

## Project Overview: AstralMart Marketing Opportunities Based on Transactional Records 
* General Overview:
    1. Describe Data
    2. Predict
    3. Decide

* Explore:
    + Customers
    + Product/Item
    + Price
    + Quantity
    + Time
    + Country

* Predict:
    + Which customers bring greatest profit to the company (largest overall invoice total)
    + Causes for Invoice Cancellations
    

```{r}
data<-read.csv("/Users/asurin/Documents/GITHUB_PUBLIC/Moxie/Online_Retail.csv")
# data5<-data[sample(nrow(data),4000),]

```
## Data Exploration: Given
<div class="columns-2">

* Qualitative Variables:
    + InvoiceNo
    + StockCode
    + Description
    + CustomerID
    + Country
    + OrderQuantitySize(small, medium, large)**
    + TotalProfitSize(small, medium, large)**
    + PurchaseSeason(Spring, Summer, Fall, Winter)**
    + TransactionType(Regular,Cancelled)**
    + Profit_Loss(Profit, Loss)**
    
* Quantitative Variables:
    + Quantity
    + Price
    + InvoiceDate
    + TotalProfitFromCustomer**

# Data Cleaning/Wrangling
```{r, echo=FALSE}
# summary(data)
# plot(data$Quantity)
# plot(data$UnitPrice)

########################################CLEAN DATA##################################################
nrow(data)

#remove trailing and leading spaces for each column
data2<-data.frame(apply(data,2, function(x){gsub("^ *|(?<= ) | *$", "", x, perl=TRUE)}))

#assign NA values to all empty fields
data2<-data.frame(apply(data2, 2, function(x){
  ifelse(is.na(x) | x == "", NA, x)
}))

data2$Quantity<-as.numeric(as.character(data2$Quantity))
data2$UnitPrice<-as.numeric(as.character(data2$UnitPrice))

#remove all values with negative UnitPrice value
data2<-data2 %>% filter(UnitPrice >= 0)

#####################################ADD Variables###########################################

######Create only good transactions
good.t<- data2 %>% filter(!grepl("^C",as.character(InvoiceNo)) & Quantity >= 0) %>% mutate(TransactionType = "Good") #531285----profit
#####Create only cancelled transaction list
canc.t<- data2 %>% filter(grepl("^C",InvoiceNo) & Quantity < 0) %>% mutate(TransactionType = "Cancelled")
#####Now Create dataset which contains only records of interest.
data2<-rbind(good.t, canc.t) %>% mutate(TransactionType=as.factor(TransactionType))


####Now assign Profit or Loss to transactions.... keep in mind that I assume here that ONLY transactions with ALL NUMERIC code is PROFITABLE all others are fees.
data2<-data2 %>% mutate(Profit_Loss = "NA")
#Now see how much money is coming in and out of the company
data2$Profit_Loss<-as.factor(ifelse(grepl("^[[:digit:]]",data2$StockCode) == TRUE, "Profit", "Loss"))

#Add seasons column
data2$InvoiceDate<-as.POSIXct(strptime(as.character(data2$InvoiceDate),
             c("%m/%d/%y %H:%M")))

Wi<- 12 # Winter
Sp<- 3 # Spring 
Su<- 6 # Summer 
Fa<- 9 # Fall 
season<-as.numeric(month(data2$InvoiceDate))
data2<-data2 %>% mutate(season=season)
data2<- data2 %>% mutate(PurchaseSeason = ifelse(season >= Wi | season < Sp, "Winter",
                                               ifelse(season >= Sp & season < Su, "Spring",
                                                      ifelse(season >= Su & season < Fa, "Summer", "Fall")))) %>% dplyr::select(-season)
data2<-data2 %>% mutate(PurchaseSeason=as.factor(PurchaseSeason))
summary(data2)


### Add TotalProfitSize per transaction
#try<-data2 %>% group_by(InvoiceNo) %>% summarise(sum(UnitPrice*Quantity))
data2<-data2 %>% group_by(InvoiceNo) %>% mutate(TotalProfitSize = sum(UnitPrice*abs(Quantity)))

### Add OrderQuantitySize per transaction
data2<-data2 %>% group_by(InvoiceNo) %>% mutate(OrderQuantitySize = sum(abs(Quantity)))
## Add OrderQantityByCountry
data2<-data2 %>% group_by(Country) %>% mutate(OrderQantityByCountry = sum(abs(Quantity)))

#ProfitByCountry
data2<-data2 %>% group_by(Country) %>% mutate(ProfitByCountry = sum(UnitPrice*abs(Quantity)))

#ProfitByCountryBySeason
data2<-data2 %>% group_by(Country,PurchaseSeason) %>% mutate(ProfitByCountryBySeason = sum(UnitPrice*abs(Quantity)))

#TotalProfitFromCustomer
data2<-data2 %>% group_by(CustomerID) %>% mutate(TotalProfitFromCustomer = sum(UnitPrice*abs(Quantity)))

# plot(data2$UnitPrice)
# p<- plot_ly(data2, y= ~UnitPrice, x= ~rownames(data2)) %>% add_markers(alpha=.02,name="alpha")

# 
# #all records where quantity is negative
# qup<-data %>% filter(Quantity<0)
# qup #10624
# #all records which were cancellations #
# qdata<-data %>% filter(grepl("^C",InvoiceNo))
# qdata#9288
# 
# data %>% filter(!grepl("^C",InvoiceNo) & Quantity >= 0)#531285----profit
# e1<-data2 %>% filter(!grepl("^C",InvoiceNo) & Quantity < 0) #1336----confused---but no price given--so junk this
# summary(e1)
# e2<-data %>% filter(grepl("^C",InvoiceNo) & Quantity < 0) #9288---lost opportunity
# summary(e2)
# data %>% filter(grepl("^C",InvoiceNo) & Quantity >=0) #0
```
## Data Exploration: Categorical Variables
<div class="columns-2">
### Transaction Types
*Transactions that were either 'Good' and 'Cancelled'
*Transactions that either provid AstralMart financial 'Profit' or 'Loss'
```{r, echo=FALSE}
#Transaction Type
pie.trans <- plot_ly(data2, labels = ~data2$TransactionType , values = ~rownames(data2), type = 'pie',
             textposition='inside',
             textinfo='label+percent')%>%
  layout(title = 'Transaction Type',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

#Transaction Type (Profit or Loss)
pie.profit<- plot_ly(data2, labels = ~data2$Profit_Loss , values = ~rownames(data2), type = 'pie',
             textposition='inside',
             textinfo='label+percent')%>%
  layout(title = 'Profit and Loss',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

#pie.profit
#pie.trans

```

### Who does AstralMart conduct most trasactions with:

```{r, echo=FALSE}
#All Good and Profit Data
g.pr.dt<-data2 %>%filter(TransactionType=="Good" & Profit_Loss=="Profit")
#All Cancelled and Profit Data
c.pr.dt<-data2 %>%filter(TransactionType=="Cancelled" & Profit_Loss=="Profit")

###Now let's look at total profitable transactions per Country EXCLUDING NEW EANGLAND
#Good
g.pr.count<-data.frame(g.pr.dt %>% group_by(Country) %>% count()) %>% mutate(Good.Count= n) %>% dplyr::select(-n)
#cancelled                       
c.pr.count<-data.frame(c.pr.dt %>% group_by(Country) %>% count()) %>% mutate(Cancelled.Count= n) %>% dplyr::select(-n)

g.c.count<- g.pr.count %>% left_join(c.pr.count, by= "Country") %>% arrange(desc(Good.Count)) %>% filter(Country != "United Kingdom")

p <- plot_ly(g.c.count, x = ~Country, y = ~Good.Count, type = 'bar', name = 'Good Transactions') %>%
  add_trace(y = ~Cancelled.Count, name = 'Cancelled Transactions') %>%
  layout(yaxis = list(title = 'Count of Profitable Transactions'), barmode = 'group')
p
#Now lets create a small plot showing New Eangland in piechart
g.c.count.2<- g.c.count %>% dplyr::select(-Cancelled.Count) %>% summarise(Total.All=sum(Good.Count))
g.c.count.3<- g.pr.count %>% left_join(c.pr.count, by= "Country") %>% arrange(desc(Good.Count)) %>% filter(Country == "United Kingdom")%>% dplyr::select(-Cancelled.Count) %>% summarise(Total.UK=sum(Good.Count))
cbind(g.c.count.2,g.c.count.3)
#TOP 10 Countries with TOP Transactions
dplyr::top_n(arrange(g.pr.count,desc(Good.Count)), 10,Good.Count )

```
### Which Country Bring most profit
```{r, echo=FALSE}
mp<-g.pr.dt %>% group_by(Country) %>% dplyr::select(Country, ProfitByCountry) %>% unique() %>% arrange(desc(ProfitByCountry)) %>% head(10)
mp


```

### Which Country Bring least profit
```{r, echo=FALSE}
lp<-g.pr.dt %>% group_by(Country) %>% dplyr::select(Country, ProfitByCountry) %>% unique() %>% arrange(ProfitByCountry) %>% head(10)
lp


```

### Which Customers Bring most profit
```{r, echo=FALSE}

mp.pie<-g.pr.dt %>% group_by(CustomerID) %>% dplyr::select(CustomerID, TotalProfitFromCustomer) %>% unique() %>% arrange(desc(TotalProfitFromCustomer)) %>% head(10)
mp.pie
pm <- plot_ly(mp.pie, labels = ~CustomerID, values = ~TotalProfitFromCustomer, type = 'pie',
              textposition='inside',
             textinfo='label+percent') %>%
  layout(title = 'Customers who Bring Least Profit',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
pm

```
### Which Customers Bring least profit
```{r, echo=FALSE}

lp.pie<-data.frame(g.pr.dt %>% group_by(CustomerID) %>% dplyr::select(CustomerID, TotalProfitFromCustomer) %>% unique() %>% arrange((TotalProfitFromCustomer)) %>% head(10))
lp.pie
pl <- plot_ly(lp.pie, labels = ~CustomerID, values = ~TotalProfitFromCustomer, type = 'pie',
              textposition='inside',
             textinfo='label+percent') %>%
  layout(title = 'Customers who Bring Most Profit',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
pl

```
### Which Products Are most Popular and Least Popular Products
```{r, echo=FALSE}
best.product<-data.frame(g.pr.dt %>% group_by(StockCode,Description) %>% count()) %>% arrange(desc(n)) %>% mutate(Stock.Total= n) %>% dplyr::select(-n) %>%  head(10)
best.product
```



### Activity Per Season
```{r, echo=FALSE}

#Purchase Season Sales
pie.season <- plot_ly(g.pr.dt, labels = ~g.pr.dt$PurchaseSeason , values = ~rownames(g.pr.dt), type = 'pie',
             textposition='inside',
             textinfo='label+percent')%>%
  layout(title = 'Activity per Season',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
pie.season
```

## Machine Learning: Approach

* General Idea:
    + Split dataset into Train (80%) and Test (20%).
    + Run different models on the Train dataset and evaluate model performance based on Test Error Rates.
    + Use the best model to find out what impacts Total Profit per Transaction

* Models used:
    + Logistic Regression
    + Classification Tree
    + Bagging Tree
    + Boosting Tree

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

data<-g.pr.dt %>% dplyr::select(-c(OrderQuantitySize,OrderQantityByCountry,ProfitByCountry,
                                ProfitByCountryBySeason,TotalProfitFromCustomer,Profit_Loss,
                                TransactionType))

refcols <- c("TotalProfitSize")
#bringing respnonse variable 'left' to the end of the dataframe
data <- data[, c(setdiff(names(data), refcols), refcols )]


#Check for NA values
data <- na.omit(data)
data<-data[sample(nrow(data),4000),]
#create test and training sets
set.seed(1)
train <- sample(1:nrow(data),.8*nrow(data))
training <- data[train,]
#select all data which is not train for test
test <- data[-train,]
#test records 'TotalProfitSize' column
actual.TotalProfitSize<-test$TotalProfitSize
```
## Machine Learning: Regression
```{r, echoe=TRUE}
###Run regular regression and look at MSE
glm.fit<-glm(as.numeric(TotalProfitSize)~., data = training)
glm.fit
pred.glm<-predict(glm.fit,test)
#MSE
mse.ols<-mean((pred.glm-test$TotalProfitSize)^2)
mse.ols

```

## Machine Learning: Tree
```{r, echo=TRUE}
treem<-tree(TotalProfitSize~., data=training)
summary(treem)
plot(treem)
text(treem,pretty = 0)
#look at the MSE
pred.tree<-predict(treem,newdata = test)
mse.tree<-mean((pred.tree-test$TotalProfitSize)^2)
#MSE
mse.tree

```



## Machine Learning: Bagging Tree
```{r, echo=TRUE}
set.seed(1)
bag.boston<-randomForest(TotalProfitSize~.,data =training, mtry=13,importance=TRUE)
bag.boston
#look at the MSE
pred.bag<-predict(bag.boston,newdata = test)
mse.bag<-mean((pred.bag-test$TotalProfitSize)^2)
#MSE
mse.bag


```
## Machine Learning: Boosting Tree
```{r, echo=TRUE}

boost.boston<-gbm(TotalProfitSize~.,data=training, distribution="gaussian", n.trees = 5000, interaction.depth=4)
summary(boost.boston)
pred.boost=predict(boost.boston, newdata=test, n.trees=5000)
#this MSE is almost exactly what random forest is
mse.boost<-mean((pred.boost-test$TotalProfitSize)^2)
#MSE
mse.boost


```

```{r, echo=FALSE}
models<-c("REG","TREE","BAGGING TREE","BOOSTING TREE")

ter.result<-c(mse.ols,mse.tree,mse.bag,mse.boost)
v3<- 1:4
ter.table<-data.frame(Classifier= models,TER_ALL = ter.result) %>% arrange(TER_ALL)


```


## Whats Next?

* Manipulate each classifier with different parameters:
    + Use CV where appropriate to obtain best performance.
* Explore different classifiers:
    + EX: Multi-Layer Neural Networks (library: neuralnet)
* Explore different visualization techniques.
* Use Python.
* Use more of the HTML and CSS to make presentation more aesthetically pleasing.

## References

1. Gareth James
    + An Introduction to Statistical Learning with Applications in R
2. Trevor Hastie
    + The Elements of Statistical Learning: Data Mining, Inference, Prediction
3. Daniel Bauer
    + Lecture Notes
